---
# YAML header created by ox-ravel
title: Preparing WAS metadata
author: Charles Berry
---
```{r  metaprep-loads, cache=2, echo=FALSE, warning=FALSE }
library(xlsx)

ngDNA <- read.xlsx(Sys.glob("*081220.xlsx"),sheetIndex=1)
ngDNA[,"CellType"][ngDNA[,"CellType"]=="CD3+ Cells"] <- "T CELLS"
ngDNA[,"CellType"] <- sub("cells","CELLS", ngDNA[,"CellType"])
ngDNA[ , "ngInput"] <- as.numeric(ngDNA[ , "ngInput"])
is.na(ngDNA[ , "ngInput"]) <- ngDNA[ , "ngInput"]<0
ngDNA[,"VCN"] <- as.numeric(ngDNA[,"VCN"])
ngDNA[,"Patient"] <- sub("pWAS000","WAS",ngDNA[,"Patient"])
pWAS.list <-
  lapply(Sys.glob("pWAS00*.RData"),
	 function(x) {
	   load(x)
	   list(d=d,sampleData=sampleData)})
pt.names <-
  sub("0+","0", sapply(pWAS.list,function(x) unique(x$d$patient)))

names(pWAS.list) <- pt.names

for (i in pt.names)
  pWAS.list[[i]]$d$cellType["CD3+ CELLS" == pWAS.list[[i]]$d$cellType] <-  "T CELLS"

pwas.time <- function(x){
  dot.for.dash <- function(x) sub("[-_]",".",x)
  d.nought <- function(x) sub("d0.*","D0",x,ignore.case=TRUE)
  d42.to.wk6 <- function(x) sub("^d4[25]$","wk6",x)
  pwas.unit <- function(x) c(WK = "WEEKS", M="MONTHS", Y="YEARS", D="DAYS")[
			     sub("[[:digit:]].*$","",x)]
  pwas.timeval <- function(x) sub("[[:alpha:]]+","",x)
  x <- as.character(x)
  tm <- toupper( d42.to.wk6( d.nought( dot.for.dash( x ))))
  res <- paste(pwas.timeval( tm ), pwas.unit( tm ))
  res[ res == "18 MONTHS" ]  <- "1.5 YEARS"
  res[ res == "30 MONTHS" ]  <- "2.5 YEARS"
  res[ res == "42 MONTHS" ]  <- "3.5 YEARS"
  res[ res == "32 DAYS" ]  <- "1 MONTHS"
  res[ res %in% c("45 DAYS", "42 DAYS") ]  <- "1.5 MONTHS"
  res[ res == "6 WEEKS" ]  <- "1.5 MONTHS"
  res
}

time.order <- function(x,pt){
  x <- as.character(x)
  y <- as.numeric(sub("[ ]+.*$","",x))
  units <- sub("^.*[ ]+","",x)
  order(pt,units,y)
}


sampleData.times <- sapply(pWAS.list,function(x) xtabs(~pwas.time(Timepoint)+CellType,x$sampleData)[,c(1,4,5,7)])

d.times <- sapply(pWAS.list,function(x) xtabs(~pwas.time(timePoint)+cellType,x$d)[,c(1,4,5,7)])


## mapply(function(x,y) setdiff(rownames(x)[rowSums(x)>0],
##			     rownames(y)[rowSums(y)>0]), sampleData.times, d.times)

times.plus <- function(x) sapply(x, function(x) rownames(x)[rowSums(x)>0])

d.times.df <-
  do.call(rbind,
	  mapply(function(x,y) data.frame(pt=x,unclass(y)),
		 names(d.times),d.times,SIMPLIFY=FALSE))

d.times.df[,"timePoint"] <- sub("pWAS[0-9]+.","",rownames(d.times.df))
d.times.df[,"pt"] <- sub("^p(WAS[0-9]+)$","\\1", d.times.df[,"pt"])


library(xlsx)

xl.path <- Sys.glob("20200608*xlsx")

wb <- loadWorkbook(xl.path)
sheets <- getSheets(wb)

## names(sheets)

## get data as list of lists with elts like:

##  ..$ 1.18 : chr "VCN Date:"
##  ..$ 1.19 : chr "CBC Date:"
##  ..$ 1.20 : chr "X- Values Not available "
##  ..$ 2.1  : chr "WAS002 1 year"

## the names index the row.column of the elts

sheet.list <- lapply(names(sheets),
		     function(nm) read.xlsx(xl.path, sheetName=nm,as.data.frame=FALSE))

## list of data.frames

## the elts in sheet.list appear here too.

sheet.list.2 <- lapply(names(sheets),
		       function(nm) read.xlsx(xl.path,
					      sheetName=nm,
					      header=FALSE,
					      as.data.frame=TRUE))

## confirm location and content of "WAS.*" text:

was.text  <-  lapply(sheet.list.2,function(sht)
  Filter(length,sapply(sht[,1:3],function(x) grep("WAS",x,value=TRUE))))


was.col2 <-
  sapply(sheet.list.2,function(sht)
    which(lengths(sapply(sht,function(x) grep("WAS",x)))>0)[2])

## data.frame(was.text[[1]][[1]],was.col2[[1]][[1]])


## look for "CD" column header rows:

sht.hdr.2 <-
  mapply( function(cl2,sht) grep("CD",sht[,cl2+3]),
	 was.col2, sheet.list.2,SIMPLIFY=FALSE)

## scrape the column names:

sht.hdr.names <-
  mapply(function(sht,hdr,cl2) sht[hdr,cl2+(3:9)],
	 sheet.list.2,sht.hdr.2,was.col2,
	 SIMPLIFY=FALSE)

## note variant spellings and/or NAs in X17 X18
names.OK <-
  sapply(sht.hdr.names,function(x) sapply(x,function(y) isTRUE(all(y[1]==y))))

names.rc <- cbind( col(names.OK)[!names.OK], row(names.OK)[!names.OK])

## these are benign - capitals, plurals or dates
## apply(names.rc,1,function(x) sht.hdr.names[[x]])


## check that row names are all the same:

sht.rw.names <-   mapply(function(sht,hdr,cl2)
    lapply(hdr, function(rw) unlist(sht[rw+(1:4),cl2])),
    sheet.list.2,sht.hdr.2,was.col2,SIMPLIFY=FALSE)


rownames.ok <- sapply(sht.rw.names,
       function(x) sapply(x,
			  function(y) isTRUE(all.equal(sht.rw.names[[1]][[1]],y))))

## all(unlist(rownames.ok))

sht.mat <-
  mapply(function(sht,hdr,cl2)
    lapply(hdr, function(rw) array(as.numeric(unlist(sht[rw+(1:4),cl2+(3:8)])),
				   c(4,6))),
    sheet.list.2,sht.hdr.2,was.col2,SIMPLIFY=FALSE)

cross.pt.time <-
  strsplit(unlist(was.text,use.names=FALSE), "(?!\\d) (?=\\d)", perl=TRUE)

cross.clean.time <- sub("-",".",
		      sub("[ S]+$","",
			  toupper( sapply( cross.pt.time, '[', 2 ))))

cross.clean.time <- ifelse(cross.clean.time=="30 DAY","1 MONTH", cross.clean.time)
cross.clean.time <- ifelse(cross.clean.time=="18 MONTH","1.5 YEAR", cross.clean.time)
cross.clean.time <- ifelse(cross.clean.time=="42 DAY","1.5 MONTH", cross.clean.time)
cross.clean.time <- ifelse(cross.clean.time=="6 WEEK","1.5 MONTH", cross.clean.time)
cross.clean.time <- paste0( cross.clean.time, "S")

cross.pt <- sub("0+","0",sapply(cross.pt.time,'[',1))
cross.clean.tab <- table( cross.clean.time, cross.pt )

## get numbers of cells counted in contam grids:
sht.mat.input <- sapply(unlist(sht.mat,recursive=FALSE),
			function(x) rowSums(x[,1:4]))
sht.rw.celltypes <- c("T CELLS", "NEUTROPHILS", "B CELLS",  "NK CELLS") 
sht.input.df <- data.frame(pt=cross.pt,time=cross.clean.time,t(sht.mat.input))
colnames(sht.input.df)[3:6]  <- sht.rw.celltypes
xl.grid.path <-  Sys.glob("Contamination grid CBC.xlsx")

gridCBC <- read.xlsx(xl.grid.path, sheetIndex=1,detectDates=TRUE)

wblk <-   grep("^W[^-]+$",gridCBC[,1])

wdash <- grep("^W.*-.*$",gridCBC[,1])

cbcPt <- sub("GT","",gridCBC[wblk[ findInterval(wdash,wblk) ], 1])

cbcTime <- sub(".* -[ ]*","",gridCBC[wdash,1])

unabbrev <- c(M=" MONTHS", Y=" YEARS",wks=" WEEKS", BSL="0 DAYS")

cbcUnit <- unabbrev[ sub("[.[:space:][:digit:]]+","",cbcTime) ]
cbcUnit[ is.na(cbcUnit) ] <- " YEARS"

cbcTime <- paste0(sub("[[:space:][:alpha:]].*$","",cbcTime),cbcUnit)
cbcTime[ cbcTime == "18 MONTHS" ] <- "1.5 YEARS"
cbcTime[ cbcTime == "6 WEEKS" ] <- "1.5 MONTHS"

## table(cbcTime,cbcPt)

common.times <- intersect(cbcTime,cross.clean.time)

## table(cbcTime,cbcPt)[common.times,] - table( was.clean.time, sapply(was.pt.time,'[',1))[common.times,]

names(gridCBC) <- c("pt.date","date.VCN","date.CBC","T CELLS","B CELLS","NK CELLS",
		    "NEUTROPHILS","comment.1","Comment.2","Comment.3")

gridCBC[,2]  <- 
  as.Date(as.numeric(gridCBC[,2])-25569, origin="1970-01-01")
gridCBC[,3]  <- 
  as.Date(as.numeric(gridCBC[,3])-25569, origin="1970-01-01")

gridCBC[,4:7]  <- lapply(gridCBC[,4:7],as.numeric)

gridCBC[wdash,"Patient"] <- cbcPt
gridCBC[wdash,"timePoint"] <- cbcTime


## contamination grid counts by sample id:

sht.tab <- ftable(xtabs(as.matrix(sht.input.df[,3:6])~pt+time,sht.input.df))
## ftable(sht.tab,row.vars=2:1)


## IS data counts - curate patient name
pwas.df <-
  do.call(rbind,
	  lapply(pWAS.list,
		 function(x) x$d[,c("patient","timePoint","cellType","estAbund")]))


pwas.df[["patient"]] <- sub(".*WAS0+","WAS0",pwas.df$patient)

pwas.tab <-
  ftable(xtabs(estAbund~pwas.time(timePoint)+patient+cellType,pwas.df),
	 row.vars=2:1)
## note times are
## D0, D0.TDX2, D0.TDX2.BAG, D0.TDX2.BAG, D32, D42, D45, M1, M1.5, M18,
## M3, M30, M42, M6, M9, Y1, Y1.5, Y2, Y2.5, Y3, Y3.5, Y4, Y4.5, Y5

ngDNA.tab <- ftable(xtabs(~pwas.time(Timepoint) + Patient +
			    toupper(CellType),ngDNA),row.vars=2:1)

## caps for cells


CBC.tab <- ftable(
  xtabs(as.matrix(gridCBC[wdash,c(4,7,5,6)])~timePoint+Patient,gridCBC[wdash,]),
  row.vars=2:1)


contam.df <- cbind(as.data.frame(sht.tab),source="contam")
is.df <- cbind(as.data.frame(pwas.tab),source="IS")
dna.df <- cbind(as.data.frame(ngDNA.tab),source="DNA")
cbc.df <- cbind(as.data.frame(CBC.tab),source="CBC")


colnames(contam.df) <- colnames(cbc.df) <-
  colnames(is.df) <- colnames(dna.df) <- 
  c("Patient", "timePoint", "CellType", "Freq", "source")

sources.df <-
  as.data.frame(
    rbind(
      as.matrix(contam.df),
      as.matrix(is.df),
      as.matrix(cbc.df),
      as.matrix(dna.df)))

sources.df[["Freq"]] <- as.numeric( sources.df[["Freq"]] )

sources.tab <- ftable(
  xtabs( I(Freq>0) ~ Patient + timePoint + CellType + source,
	sources.df),
  col.vars=4)


four.celltypes <- c("T CELLS", "B CELLS","NEUTROPHILS", "NK CELLS")

sources.tab1 <-
  xtabs( I(Freq>0) ~ Patient + timePoint + CellType + source,
	sources.df,subset=CellType %in% four.celltypes)


pt.tm <- apply(sources.tab1,c(1,2),sum)


pt.tm.complete <- subset(as.data.frame.table(t(pt.tm)==16),Freq==TRUE)

library(cellTypeCompositions)

wttabs <- list()

for (i in 1:nrow(pt.tm.complete)){
  pt <- paste0("p",pt.tm.complete[i,"Patient"])
  tm <- as.character(pt.tm.complete[i,"timePoint"])
  tab <- xtabs(estAbund~posid+cellType,
	       pWAS.list[[pt]]$d,
	       subset=cellType %in% four.celltypes & pwas.time(timePoint)==tm)
  wttabs[[i]] <- uniTab(tab)
}

pt.tm.names <-
  make.names(
    with(pt.tm.complete,paste(Patient,timePoint,sep=",")))

wt.ct.names <- colnames(wttabs[[1]]$tab)

pre.counts <- list()
for (i in 1:nrow(pt.tm.complete)){
  pt <- as.character(pt.tm.complete[i,"Patient"])
  tm <- as.character(pt.tm.complete[i,"timePoint"])
  cnts <- subset(gridCBC,
		 subset=Patient == pt & timePoint==tm,
		 select=wt.ct.names)
  pre.counts[[i]] <-
    cnts * ifelse(wt.ct.names == "NEUTROPHILS", 1000,1)
}

cross.ct.order <- match(wt.ct.names,sht.rw.celltypes)

cross.counts <- list()
for (i in 1:nrow(pt.tm.complete)){
  Patient <- as.character(pt.tm.complete[i,"Patient"])
  tm <- as.character(pt.tm.complete[i,"timePoint"])
  pt.indx <- match(Patient, as.character(unique(sht.input.df$pt)))
  tm.indx <- match(tm, with(sht.input.df,time[Patient == pt]))
  cnts <- sht.mat[[pt.indx]][[tm.indx]][cross.ct.order,cross.ct.order]
  cross.counts[[i]] <- cnts
}


dna.wts <- list()
for (i in 1:nrow(pt.tm.complete)){
  pt <- as.character(pt.tm.complete[i,"Patient"])
  tm <- as.character(pt.tm.complete[i,"timePoint"])
  df <- subset(ngDNA,
	       subset=pt==Patient & pwas.time(Timepoint) == tm)

  dna.wts[[i]] <- df[match(wt.ct.names,toupper(df$CellType)),
		     c("ngInput","corrected.nginput","VCN")]

}

## mis-class probs estimated separately
mcs <- mapply(
  function(x,y) {
    pre <- diag(prop.table(x[1,]))
    cross <- prop.table(y,1)
    t( prop.table( pre %*% cross, 2))
  }, pre.counts,cross.counts,
  SIMPLIFY=FALSE)

## estimated by combining counts from different samples
## t(prop.table(diag(Reduce("+",pre.counts))%*% prop.table(Reduce("+",cross.counts),1),2))

## estimated by smoothing to Dirichlet prior
mcs2 <-
  mapply(
    function(x,y) {
      pre <- diag(prop.table(x[1,]))
      cross <- prop.table(y+0.1,1)
      t( prop.table( pre %*% cross, 2))
  },
  pre.counts,cross.counts,
  SIMPLIFY=FALSE)


psi <- mapply(function(pre,wt) {
  y <- wt$corrected.nginput/unlist(pre)
  y/max(y)}, pre.counts,dna.wts,SIMPLIFY=FALSE)

om <- mapply(function(post,cross) cross%*%diag(post),
	     psi,mcs2,SIMPLIFY=FALSE)

psi2 <- mapply(function(tab,wt,pre) {
  y <- colSums(tab$tab*tab$n)/as.numeric(wt$VCN)
  y <- y/pre
  y/max(y)
}, wttabs, dna.wts,pre.counts,SIMPLIFY=FALSE)

om2 <- mapply(function(post,cross) cross%*%diag(post),
	     psi2,mcs2,SIMPLIFY=FALSE) 
```

The aim of this document is provide a description of

1.  The construction a depletion matrix that quantifies the relative
    frequencies with which cells of a given type are sequenced for
    integration site (IS) detection.

2.  Further curation of metadata files used in that matrix.


# Metadata files

The metadata for the analysis of cell type composition in WAS patients
comes in three files:

-   **DNA amounts:** From the file `r paste0("\U0060",Sys.glob("*081220.xlsx"),"\U0060") `

-   **Pre-Sort Cell Proportions:** From the file `Contamination grid CBC.xlsx`

-   **Post-sort Counts:** From the file `r paste0("\U0060",Sys.glob("20200608*xlsx"),"\U0060") `

As is obvious, these files are EXCEL spreadsheets and come with the
usual assortment of defects and inconsistencies associated with such
hand-crafted documents.  The correction of these is necessary to use
the data in the files in any programmatic fashion. To this end, I
establish consistent sets of

1.  Timepoint names
2.  Cell Type names
3.  Patient Names

These names are used to establish mappings from one file to another
and to the `*.RData` files found at <http://bushmanlab.org/> in the
`data/export/projects/gtVISA/Boston_WAS/subjectReports/` directory and
the data elements within them.  In addition, these files require some
further curation to get consistency.


# DNA Amounts

Initially, the DNA amounts file is read in using the `xlsx::read.xlsx`
R function.

-   In the `CellType` column `CD3+ Cells` is changed to `T CELLS`

-   The word `cells` is rendered in upper case when it appears in the
    `CellType` column

-   The `ngDNA` column is converted to numeric mode and values less than
    zero are rendered as `NA`.

-   The `VCN` column is converted to numeric.

-   The `Patient` column entries are rendered as `WAS0d` wehere `d` is
    one of 2, 3, 4, 5, or 6.


# pWAS000\*.RData files

The `*.RData` files are read in. Each of these has a collection of
objects, but only two are of interest here.

-   **d:** a `data.frame` containing information about the integration
    sites: `posid` (the IS identifier), `CellType`, `timePoint` and
    `estAbund` (the presumed number of cells sharing that `posid`,
    `CellType` and `timePoint` )

-   **sampleData:** a `data.frame` giving some details of the samples

These files are read as a single list containing one element for each
file which is a list with elements `d` and `sampleData`.

The patient names for the corresponding list elements are extracted as
the unique value of `d$patient` and rendered in the same format as
used in the DNA Amount `Patient` column.

The times in the `d$timePoint` columns are revised as follows:

-   use decimals, not dashes or underscores to denote decimal fractions
-   use `MONTHS` and `YEARS` as the time units except for `D0`
-   let 42 and 45 days each be `1.5 MONTHS`


# Post-sort Counts

The file `r paste0("\U0060",Sys.glob("20200608*xlsx"),"\U0060") `
contains multiple *sheets* which are read in as a list of `data.frame`
objects.  These require further scraping to identify each block that
displays counts of sorted cells according to their presumed cell types
and to determine to which time point each block pertains.

Times are rendered as for the `pWAS000*.RData`. Aftering upcasing
times, `30 DAY` becomes `1 MONTHS`. `6 WEEK` becomes `1.5 MONTHS`

Patient names are rendered as for the `pWAS000*.RData`.

The matrices that are scraped from the file consist of the first four
columns of counts and are labelled with cell types `T CELLS`,
`NEUTROPHILS`, `B CELLS` and `NK CELLS` as are the rows.


# Pre-sort Counts

The pre-sort counts file, `Contamination grid CBC.xlsx`, is read as a
single `data.frame`.

Further scraping is required to isolate components associated with
different samples and patients.

Again, the sampling times are rendered as described above.

The cell types are assigned labels `T CELLS`, `NEUTROPHILS`, `B CELLS`
and `NK CELLS`.


# Combining Data Sources

A collection of tables derived from the above is used to determine
those samples having data for all four cell types for every data
source.  These samples for which this is true are:

```{r  echo=FALSE, comment="" }
print(
  pt.tm.complete[,1:2][
    with(pt.tm.complete,
	 order(Patient,sub(".* ","",
			   as.character(timePoint)))),],
  row.names=FALSE) 
```


# Calculation of the Depletion Matrix

The depletion matrix is based on three components:

-   **\(\Upsilon\):** the vector of cell type specific constants for
    pre-sort cell depletion. Any reduction due to sample processing in
    the frequency of cells of a particular type before cell sorting is
    reflected in this vector. For the purpose of this study, these
    values are assumed to be 1.0.  This is because no data were
    obtained to track the cell type specific depletion of the sample/

-   **\(\Omega\):** the matrix of cell sorting probabilities. The
    canonical element of this matrix give the probability that a cell of
    a specific type ends up in a sorter tube intended for that or
    another cell type.  These values are ascertained from the post-sort
    retabulations of cell types and the pre-sort frequencies.

-   **\(\Psi\):** the vector of cell type specific constants
    for post-sort cell depletion. Any reduction due to sample
    processing in the frequency of cells from a particular sorter tube
    after cell sorting and before and during sequencing to deterimine
    ISs is reflected in this vector.

With these values in hand, the depletion matrix is given by

\[\Phi = \mathrm{Diag}(\Upsilon)\Omega\mathrm{Diag}(\Psi)
\]

where \(\mathrm{Diag}(x)\) produces the diagonal matrix with \(x\) as its diagonal. 


## Calculation of  post sort depletion constants, \(\Psi\)

The post-sort depletion constants are proporitonal to the ratios of
\(z\), the sample cell counts, divided by \(w\), the amounts of DNA
submitted for processing to determine ISs. The absolute values of the
constants cannot be determined, but for present purposes the relative
values suffice. The values are normalized so that their maximum is 1.0, viz.

\[\Psi_j = \frac{w_j/z_j}{\max_i w_i/z_i}
\]

\(z\) has elements \(z_i = \#(\mbox{cells in tube}~ i)\) and
\(\#(\cdot)\) denotes the count of elements to satisfy the condition
given as the argument.

As an example, here are the cell counts, corrected DNA weights, and
computed weights, \(\Psi\):

```{r   }

example.wts <-
  dna.wts[[1]]$corrected.nginput/pre.counts[[1]]
example.wts <- example.wts/max(example.wts)

print(
  rbind("Pre-sort"=pre.counts[[1]],
	ngInput=dna.wts[[1]]$corrected.nginput,
	weights=example.wts),digits=3)
 
```

An alternative to this method uses estimates of the vector copy number
(texttt{VCN}) for each cell type, counts of cells sampled and the
counts of IS copies for the sample. Again, this is normalized so the
;largest value is 1.0:

\[\Psi_j = \frac{N_j/(\texttt{VCN}_j z_j)}{max_i \left(N_i/(\texttt{VCN}_i z_i)\right)}
\]

\(N\) has elements \(N_i = \#(\mbox{IS bearing fragments in tube}~ i)\)

As an example, here are the fragment counts (\(N\)), pre-sort cell counts, vector copy numbers, and
computed weights, \(\Psi\) for the same sample just shown:

```{r  echo=FALSE, comment="" }

example.frags <- with(wttabs[[1]],colSums(tab*n))

example.wts <-
  example.frags/pre.counts[[1]]/dna.wts[[1]]$VCN
example.wts <- example.wts/max(example.wts)

print(
  rbind("Pre-sort"=pre.counts[[1]],
	N = example.frags,
	VCN=dna.wts[[1]]$VCN,
	weights=example.wts),digits=3) 
```

As is evident, the values of \(\Psi\) are in rough agreement.  We will
consider the impact using one of these two estimates versus the other
in a later document.


## Calculation of Sorting Probabilities

The sorting probabilities, \(\Omega\) are computed from a table of
counts, \(X\), and a vector of sample cell counts, \(z\).

\(X\) has elements like

\[X_{ij} = \#(\mbox{cells in tube}~ i ~\mbox{counted as type}~ j) 
\]

\[\Omega = \mathrm{Diag}(X'z)^{-1}X'\mathrm{Diag}(z)
\]

As an example, here the cell type recounts for the sample used
previously:

```{r  echo=FALSE, comment="" }
example.mat <- cross.counts[[1]]
dimnames(example.mat) <- list(tube=wt.ct.names,recount=wt.ct.names)
example.mat 
```

Applying the pre-sort counts, \(\Omega\) is

```{r  echo=FALSE, comment="" }
example.mat <- mcs[[1]]
dimnames(example.mat) <-list("CellType"=wt.ct.names,tube=wt.ct.names)
print(example.mat,digits=3) 
```

Using the first value of \(\Psi\) from above, we have as the depletion matrix, \(\Phi\):

```{r  echo=FALSE, comment="" }
example.mat <- mcs[[1]]%*%diag(psi[[1]])
dimnames(example.mat) <-
list("Sample"=wt.ct.names,Sequencer=wt.ct.names)
print(example.mat,digits=3) 
```

